Smart Model Elimination for Efficient Automated Machine Learning

### 2024-06-23 paper/paper.tex
Update paper.tex

Taking a closer look at four AutoML standards, we can observe pros and cons in their theoretical application to medicine and research. FLAML uses blend search hyper-parameter optimization and focuses on lightweight models, making it quick and applicable to repetitive tasks in the medical sphere. It supports imputation techniques for missing values with user specification and has an intuitive API, making it moderately user-friendly for minimally trained healthcare workers [9, 12]. H2O has a wider variety of supported algorithms that may or may not be appropriate for medical diagnosis, making it slower than FLAML on average. In one trial, more than half of FLAML's performances in one minute were better than or equal to H20's performances in one hour [12]. H2O has automatic and multi-faceted methods of dealing with missing values and flexible interfaces in R and Python, making it intuitive for users [5]. MLJAR uses more advanced algorithms such as light gradient boosting and neural networks. It automatically deals with missing values and is known for its automated user interface [7, 8]. TPOT uses genetic programming. It builds pipelines over multiple generations, which can be time consuming. It has built-in pre-processing for missing values, but the genetic programming can require fine-tuning from users [6, 8].

>>>>

Taking a closer look at four AutoML standards, we can observe pros and cons in their theoretical application to medicine and research. FLAML uses blend search hyper-parameter optimization and focuses on lightweight models, making it quick and applicable to repetitive tasks in the medical sphere. It supports imputation techniques for missing values with user specification and has an intuitive API, making it moderately user-friendly for minimally trained healthcare workers [9]. H2O has a wider variety of supported algorithms that may or may not be appropriate for medical diagnosis, making it slower than FLAML on average. In one trial, more than half of FLAML's performances in one minute were better than or equal to H20's performances in one hour [9]. H2O has automatic and multi-faceted methods of dealing with missing values and flexible interfaces in R and Python, making it intuitive for users [5]. MLJAR uses more advanced algorithms such as light gradient boosting and neural networks. It automatically deals with missing values and is known for its automated user interface [7]. TPOT uses genetic programming. It builds pipelines over multiple generations, which can be time consuming. It has built-in pre-processing for missing values, but the genetic programming can require fine-tuning from users [6].
